Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd

@@

In contrast, White and American Indian or Alaska Native groups are predicted to vote more for Trump in comparison to Biden. This is interesting they are different from many other minority groups, who strongly prefer Biden rather than trump. In an article by the CNBC written by Myong (2020), American Indian or Alaska Natives are considered to be a key demographic as they could help swing votes in as many as 7 states. This could explain the why the votes are predicted to be split between Trump and Biden, as both parties are putting a focus on gaining these votes. Similarily with the White population, as they represent the vast majority of citizens in USA, they will be the target race demographic for both Trump and Biden as they both fight for what is predicted to be a close election race.

>>>>

As discussed in the results, race can play a significant factor in predicting an individuals vote in the 2020 election. As shown in Figure N, 90% of African American or Black voters are projected to vote for Biden, with Asian voters follow closely with almost 80% of Chinese voters projected to vote for Biden. Given Trump's response to the Black Life's Matter movement, and his response to Coronavirus (China virus according to him), it seems clear that voters belonging to these groups feel strongly against him. There has been protests and outrage country wide in response to police brutality leading to the deaths of black or  African American citizens, many protesters feel President Trump is ignoring their voice, focusing on the riots and ignoring the multitude of peaceful protests also happening, going as far as implying the movement is a "symbol of hate (@trump_blm)." The same article brings up other acts of Trump, such as re-tweeting videos of supporter chanting "White power", Trump diminishing the notion of Black Lives Matter by correcting it into All Lives Matter,  and defending an individual who was accused and convicted of shooting and killing 2 black lives matter protesters (@trump_kyle). Googling the words Trump and Black Lives Matter results in pages upon pages of news articles, blog posts and tweets of President Trump seemingly repeatedly condemning Black Lives Matter supporters and supporting anti-black lives matter movements. Whether or not these articles have taken his words out of context and twisted his words around, it seems clear that Trump is labeled to be "anti-black" and our predictions indicate that these feelings among the Black and African American community will reflect heavily on their votes, with less than 10% projected to be voting for Trump. Another major issue is the global pandemic caused by the SARS-CoV-2 virus (or according to Trump, the China Virus). Asian American's live in fear of xenophobia and other racist attacks, as many interviewed in the New York Times article (@chinese_safety) recounts racist attacks and comments, many calling for Trump to stop targeting China. The Vancouver police has reported a 600% increase in reports of hate crimes against the Asian community, and while this is not in the USA, it's obvious that Asians living in the USA has decided to hedge their support towards Biden. Of course there are many reasons that affect an individual's decision to vote, but these recent and relevant events may be one of the reasons that voters of Asian and Black or African American races are supporting Joe Biden in the upcoming election. In general, all ethnic minorities (with the exception of American Indian or Alaska Native) support Biden more to various degrees.

@@

In contrast, White and American Indian or Alaska Native groups are predicted to vote more for Trump in comparison to Biden. This is interesting they are different from many other minority groups, who strongly prefer Biden rather than trump. In an article by the CNBC written by @native_vote, American Indian or Alaska Natives are considered to be a key demographic as they could help swing votes in as many as 7 states. This could explain the why the votes are predicted to be split between Trump and Biden, as both parties are putting a focus on gaining these votes. Similarily with the White population, as they represent the vast majority of citizens in USA, they will be the target race demographic for both Trump and Biden as they both fight for what is predicted to be a close election race.

## Education
